A novel method for detecting coalescing binaries in near realtime with Advanced LIGO and beyond \editorial{Submit to PRD or CQG?}

### 2011-02-19 appendix.tex
added floating point operation count table
git-svn-id: https://svn.ligo.caltech.edu/svn/6th-Floor-Papers/lloid_paper@655 ccdd05d5-56c1-461a-bf98-85f6876523b4

\editorial{I just yanked this from the methods section.  It needs to be made more concise, maybe turned into a table of CPU budgets for various components of LLOID.} The filter bank can be implemented using finite impulse response (\textsc{fir}) filters, which are just sliding window dot products.  If there are $M$ templates of length $n$, and the data stream contains $N$ samples, then applying the filter bank requires $2 M N n$ operations.

>>>>

Each addition and each multiplication is counted as a single floating point operation.   We are not assuming that a multiply-accumulate is available as a single operation.

\begin{table}[htdp]
\caption{Number of floating point operations per sample (multiplications and divisions) required for a selection of signal processing operations used in \textsc{lloid}.}
\begin{center}
\setlength{\extrarowheight}{6pt}
\begin{tabular}{l c}
\hline
Process & ops/sample \\
\hline\hline
\textsc{fir} matched filter, M templates of length $n$ & $2 M n$ \\\hline
\textsc{fft} matched filter, M templates of length $n$, blocks of length $D$ & $\frac{4 (M + 1) \lg D + 2 M}{1 - n/D}$ \\\hline
$n$ tap \textsc{fir} resampling filter, sample rates $f_1 < f_2$ & $2 M n f_1 / f_2$ \\\hline
multiply $M \times L$ real matrix by $L\times1$ real vector & $2 M L$ \\\hline
\end{tabular}
\end{center}
\label{table:flops}
\end{table}%

The filter bank can be implemented using finite impulse response (\textsc{fir}) filters, which are just sliding window dot products.  If there are $M$ templates of length $n$, and the data stream contains $N$ samples, then applying the filter bank requires $2 M N n$ operations.
